---
title: "CINmetrics_analysis_SexBias"
author: "Tabea M. Soelter"
date: "3/7/2022"
output: html_document
---
### Analysis of Sex Differences across TCGA cancers

# Load packages
```{r}
library(CINmetrics)
library(tidyverse)
library(ggpubr)
library(here)
library(ComplexHeatmap)
library(circlize)
library(reshape2)
library(rstatix)
library(lintr)
library(styler)
library(here)
```

# Source functions
```{r}
source(here("src", "functions_CINmetrics_Cancer_Sex_Analysis.R"))
```

# Load data processed by S.T.
```{r}
# load all_cancer_df
all_cancer_df <- read.csv(here("data", "processed", "all_cancer_df.csv"))
```

# Calculate CINmetrics
* Calculate for all cancers 
* Include gender metadata and rename it to sex
* Removing any samples that did not report sex
```{r}
# calculate CINmetrics (takes a long time, but can be run locally)
all_cinmetrics_sex_df <- get_cinmetrics(all_cancer_df)

# check gender column for NAs and remove
sum(is.na(all_cinmetrics_sex_df$gender)) # 95
all_cinmetrics_sex_df <- na.omit(all_cinmetrics_sex_df)

# check for samples that did not report gender
sum(all_cinmetrics_sex_df$gender == "not reported") # 4
all_cinmetrics_sex_df <- subset(all_cinmetrics_sex_df, gender != "not reported")
sum(all_cinmetrics_sex_df$gender == "not reported") # 0

# rename gender column to "sex"
names(all_cinmetrics_sex_df)[names(all_cinmetrics_sex_df) == "gender"] <- "sex"
```

# Calculate p-values
* Wilcoxon test on all cancers with respect to sex
* Bonferroni correction
```{r}
# Create list of all cancer projects
# removed OV, PRAD, UCEC, TGCT, CESC, UCS due to lack of data
cancer_project <- c("TCGA-GBM",
                    "TCGA-LUAD",
                    "TCGA-LUSC",
                    "TCGA-BLCA",
                    "TCGA-ESCA",
                    "TCGA-PAAD",
                    "TCGA-KIRP",
                    "TCGA-LIHC",
                    "TCGA-SARC",
                    "TCGA-BRCA",
                    "TCGA-THYM",
                    "TCGA-MESO",
                    "TCGA-COAD",
                    "TCGA-STAD",
                    "TCGA-SKCM",
                    "TCGA-CHOL",
                    "TCGA-KIRC",
                    "TCGA-THCA",
                    "TCGA-HNSC",
                    "TCGA-LAML",
                    "TCGA-READ",
                    "TCGA-LGG",
                    "TCGA-DLBC",
                    "TCGA-KICH",
                    "TCGA-ACC",
                    "TCGA-PCPG",
                    "TCGA-UVM"
                    )

# Make list of metrics to include
metrics <- c("tai",
             "modified_tai",
             "cna",
             "base_segments",
             "break_points",
             "fga")

# Perform stats test using Wilcoxon rank
sex_utest_df <- get_utest_data(all_cinmetrics_sex_df, cancer_project, metrics)
```

# Bar plot for all cancers
* Bar plot of -log10 transformed p values of wilcoxon tests between sexes for all cancers
```{r}
# plot bar plots
sex_barplot <- get_utest_graphs()
sex_barplot

# save bar plots
ggsave(sex_barplot,
       filename = here("results",
                       "cin_sex_barplot_all.pdf"),
       width = 8.5,
       height = 11)
```

# Combined plots
* Bar plots of top 1-0 most significant cancers
* Rain cloud plots for the top 1 most significant cancer 
```{r}
# generate bar and rain cloud plots
sex_barplot_raincloud <- get_utest_combined_graphs(sex_utest_df = sex_utest_df,
                                                   all_cinmetrics_sex_df = all_cinmetrics_sex_df
                                                   )
sex_barplot_raincloud

# save plot
ggsave(sex_barplot_raincloud,
       filename = here("results",
                       "cin_sex_bar_raincloud.pdf"),
       width = 8.5,
       height = 11)
```

# Session Info
```{r}
sessionInfo() # see output below
```
R version 4.1.2 (2021-11-01)
Platform: x86_64-apple-darwin17.0 (64-bit)
Running under: macOS Monterey 12.4

Matrix products: default
LAPACK: /Library/Frameworks/R.framework/Versions/4.1/Resources/lib/libRlapack.dylib

locale:
[1] en_US.UTF-8/en_US.UTF-8/en_US.UTF-8/C/en_US.UTF-8/en_US.UTF-8

attached base packages:
[1] grid      stats     graphics  grDevices utils     datasets  methods   base     

other attached packages:
 [1] ggprism_1.0.3         PupillometryR_0.0.4   rlang_1.0.6           gghalves_0.1.1        cowplot_1.1.1         styler_1.9.1         
 [7] lintr_3.0.2           rstatix_0.7.0         reshape2_1.4.4        circlize_0.4.15       ComplexHeatmap_2.13.1 here_1.0.1           
[13] ggpubr_0.4.0          forcats_0.5.1         stringr_1.4.0         dplyr_1.0.9           purrr_0.3.4           readr_2.1.3          
[19] tidyr_1.2.0           tibble_3.1.7          ggplot2_3.3.6         tidyverse_1.3.1       CINmetrics_0.1.0     

loaded via a namespace (and not attached):
 [1] colorspace_2.0-3    ggsignif_0.6.3      rjson_0.2.21        ellipsis_0.3.2      rprojroot_2.0.3     GlobalOptions_0.1.2 fs_1.5.2           
 [8] clue_0.3-61         rstudioapi_0.13     farver_2.1.0        remotes_2.4.2       bit64_4.0.5         fansi_1.0.3         lubridate_1.8.0    
[15] xml2_1.3.3          codetools_0.2-18    R.methodsS3_1.8.1   doParallel_1.0.17   knitr_1.39          jsonlite_1.8.0      broom_1.0.1        
[22] cluster_2.1.2       dbplyr_2.1.1        png_0.1-7           R.oo_1.24.0         compiler_4.1.2      httr_1.4.3          backports_1.4.1    
[29] assertthat_0.2.1    fastmap_1.1.0       lazyeval_0.2.2      cli_3.3.0           htmltools_0.5.2     tools_4.1.2         gtable_0.3.0       
[36] glue_1.6.2          Rcpp_1.0.8.3        carData_3.0-5       cellranger_1.1.0    vctrs_0.4.1         iterators_1.0.14    xfun_0.31          
[43] ps_1.7.1            rvest_1.0.2         lifecycle_1.0.1     scales_1.2.0        vroom_1.6.0         hms_1.1.1           rex_1.2.1          
[50] parallel_4.1.2      RColorBrewer_1.1-3  yaml_2.3.5          gridExtra_2.3       stringi_1.7.6       S4Vectors_0.32.4    desc_1.4.1         
[57] foreach_1.5.2       BiocGenerics_0.40.0 cyclocomp_1.1.0     shape_1.4.6         pkgconfig_2.0.3     matrixStats_0.62.0  evaluate_0.15      
[64] labeling_0.4.2      bit_4.0.4           tidyselect_1.1.2    processx_3.6.1      ggsci_2.9           plyr_1.8.7          magrittr_2.0.3     
[71] R6_2.5.1            IRanges_2.28.0      generics_0.1.2      DBI_1.1.2           pillar_1.7.0        haven_2.4.3         withr_2.5.0        
[78] abind_1.4-5         modelr_0.1.8        crayon_1.5.1        car_3.1-0           utf8_1.2.2          tzdb_0.3.0          rmarkdown_2.11     
[85] GetoptLong_1.0.5    readxl_1.3.1        callr_3.7.0         reprex_2.0.1        digest_0.6.29       R.cache_0.16.0      R.utils_2.11.0     
[92] stats4_4.1.2        munsell_0.5.0

# Reproducibility
```{r}
# styler
style_file(here("src",
                "220302_CINmetrics_analysis_SexBias.Rmd"))

# lintr
lint(filename = here("src",
                     "220302_CINmetrics_analysis_SexBias.Rmd"))
```


